\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}       %makes text copy-and-pastable
\usepackage{wrapfig}           %for figures
\usepackage{graphicx}          %for images
\usepackage{booktabs}          % good tables package
\usepackage{array}             %for spacing tables
\usepackage{multirow}          %for multirow tables
\usepackage{caption}           %for the captionof command
\usepackage{amsmath}           %for any moderately complex math
\usepackage{placeins}          %allows us to use \FloatBarrier
\usepackage{caption}           %to use minipage for inserting figures
\usepackage{float}             %for H figure and table placements Here.
\usepackage{comment}          %for bulk comments
\usepackage[colorinlistoftodos]{todonotes}%to do notes
\usepackage[parfill]{parskip}  %To use blank lines instead of indentation to separate paragraphs
\usepackage{ifthen}            %ifthenelse command
\usepackage[margin=3cm]{geometry} %Change margin size
\usepackage{titling}           %for spacing the title
\usepackage{blindtext}         %for spacing the title
    \setlength{\droptitle}{-4em}     % For spacing the title
    \addtolength{\droptitle}{-4pt}   % For spacing the title
%\usepackage[super]{nth}        %write 1st,2nd,3rd with \nth{1},\nth{2}, \nth{3}
%\usepackage{ifdraft}
\usepackage{units}
\usepackage{subcaption} % for subfigures
\captionsetup{width=0.8\textwidth}


\usepackage{tikz}
\usepackage{calc}
% \usepackage{pgfgantt}             %For gantt charts
\usepackage{pgffor}
\usepackage[american]{circuitikz}
\usepackage{ifthen}
\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usetikzlibrary{decorations.pathreplacing}

\usepackage{varioref}

\usepackage[hidelinks,%clickable cross references and URLs
            pdftex,%pdf meta data
            pdfauthor={Matthew Davis},%pdf meta data
            pdftitle={ELEC4614 2013 Solutions},%pdf meta data
            %pdfsubject={\@title},%pdf meta data
            pdfkeywords={UNSW, ELSOC, ELEC4614, Power, Electronics, Past, Paper, Exam, Solutions, supp, supplementary}]{hyperref}

\usepackage[nameinlink, capitalise, noabbrev]{cleveref}

\title{ELEC4614 2013 S1 Supplementary Exam Solutions}
\author{Matthew Davis \\ \href{mailto:vicepresident@elsoc.net}{vicepresident@elsoc.net}}

\renewcommand\thesection{Question \arabic{section}}
\renewcommand\thesubsection{(\alph{subsection})}
\renewcommand\thesubsubsection{\roman{subsubsection})}

\usepackage{tocloft}
\usepackage{chngcntr}
\setlength{\cftsecnumwidth}{6em}
%\setlength{\cftsubsecnumwidth}{3.25em}
\setlength{\cftsubsubsecnumwidth}{4em}




\begin{document}

\maketitle

\begin{abstract}
    These are the unofficial solutions to the 2013 Semester 1 Power Electronics exam.
    There are two different 2013 exams. 
    These solutions abre for the one where question 1a has an inductor, which is the supplementary exam.
    The other exam is available on the library website.
    This is just the first draft. I don't guarantee than the solutions here are correct. If you spot a mistake, please let me know. I've put orange boxes throughout to indicate where I'm unsure.
    More solutions, papers and notes can be found at \href{www.elsoc.net}{elsoc.net}.
    Please note that for this particular exam, you only needed to solve 4 out of 6 possible questions.
\end{abstract}

%\listoftodos

\tableofcontents

\include{1/main}
\include{2/main}
\include{3/main}
\renewcommand\thesubsection{(\roman{subsection})}
\include{4/main}
\renewcommand\thesubsection{(\alph{subsection})}
\include{5/main}
\include{6/main}


\end{document}
